Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-06-06 template.tex
added some proofs to the paper, working on Ers(t) imag part

\item Let $x(t) * y(t)$ represent the convolution of two functions $x(t)$ and $y(t)$.  Let the envelope of the convolution be $\mathcal{E}_{x * y}(t)$.  $\mathcal{E}_{x * y}(t)$, $x_a(t)$, and $y_a(t)$ are related by

@@

\mathcal{E}_{x * y}(t) = \frac{1}{2}| x_a (t) * y_a(t)| \label{eq:awesome}

@@

We should include the proof here (I have to track it down in my notebooks).
\item The analytic signal of the Askaryan pulse is given by Eq. \ref{eq:sa_4}.  The RLC damped oscillator response and corresponding analytic signal are

@@

r(t) &= R_0 e^{-\gamma t} \cos(2\pi f_0 t) \\
r_a(t) &= R_0 e^{-\gamma t} e^{2\pi j f_0 t} \label{eq:ra}

@@

The parameter $\gamma$ is the \textit{decay constant}, and the parameter $f_0$ is the resonance frequency.  Note that the envelope of $r(t)$, $|r_a(t)|$, is simply $R_0 \exp(-\gamma t)$, as it should be.  The proof of Eq. \ref{eq:ra} is as follows:

@@

r(t) &= R_0 e^{-\gamma t} \cos(2\pi f_0 t) \\
R(f) &= \frac{R_0}{2\pi j} \left( \frac{f - \frac{j\gamma}{2\pi}}{(f-z_+)(f-z_-)} \right) \\
z_+ &= f_0 + \frac{j\gamma}{2\pi} \\
z_- &= -f_0 + \frac{j\gamma}{2\pi} \\
\widehat{r}(t) &= \mathcal{F}^{-1}\left \lbrace - j \sgn(f) R(f) \right \rbrace \label{eq:rh} \\ 
\widehat{r}(t) &= \frac{R_0}{2j}\left( e^{2\pi j f_0 t} - e^{-2\pi j f_0 t} \right) e^{-\gamma t} \\
\widehat{r}(t) &= R_0 \sin(2\pi f_0 t) e^{-\gamma t} \\
r_a (t) &= R_0 \left(\cos(2\pi f_0 t) + j\sin(2\pi f_0 t)\right) e^{-\gamma t} \\
r_a (t) &= R_0 e^{2\pi j f_0 t} e^{-\gamma t}

@@

In evaluating the inverse Fourier transform in Eq. \ref{eq:rh}, the poles at $z_+$ and $z_-$ must be enclosed in separate contour integrals.

@@

r_a(t) * \Re\lbrace s_a(t) \rbrace = \int_0^{\infty} r(\tau) s(t-\tau) d\tau

@@

Subsituting Eq. \ref{eq:fadd} into Eq. \ref{eq:conv}, and simplifying, produces

@@

-j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz}
Finally, the derivative of the Faddeeva function is $dw/dz = 2j/\sqrt{\pi} - 2 zw(z)$.  Substituting for $dw/dz$ gives the final result:
+ R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2}(1+j\sqrt{\pi} z w(z)) \label{eq:Re_result}

@@

\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= R_0\int_{-\infty}^{\infty} e^{-zt} e^{-2\pi j ft} dt \\

@@

\sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) + \\
R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2}(1+j\sqrt{\pi} z w(z)) + \\
j\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + \\
j\sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:final}

@@

The units of the convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq.\ref{eq:final} has these units.  The first term is proportional to $R_0 \sigma_t s(t)$, and $s(t)$ has units of $E_0 \sigma_t$, so the unit product is $R_0 E_0\sigma_t^2$.  The units of the second term are $R_0 E_0\sigma_t^2$.  The third term has units of $E_0\sigma_t^2 r_a(t)$, and $r_a(t)$ has units of $R_0$, so the unit product is $R_0 E_0\sigma_t^2$.  The fourth term has units of $R_0 \sigma_t s(t)$, like the first term.  Thus, all units check.  To check the limits, the parameters within $z$ and $z_1$ must be recalled.  Combining prior definitions, the results are

>>>>

\item Let $s(t) * r(t)$ represent the convolution of $s(t)$ and $r(t)$.  Let the envelope of the convolution be $\mathcal{E}_{s * r}(t)$.  $\mathcal{E}_{s * r}(t)$, $s_a(t)$, and $r_a(t)$ are related by

@@

\mathcal{E}_{s * r}(t) = \frac{1}{2}| s_a (t) * r_a(t)| \label{eq:awesome}

@@

The proof of Eq. \ref{eq:awesome} is based on two ideas.  First, the Hilbert transform of a function $s(t)$ is equivalent to convolving it with the ``tempered distribution'' $h(t) = 1/(\pi t)$.  Second, computing the Hilbert transform twice yields the original function, multiplied by $-1$: $h * h * s = -s$.  Given the definitions of the analytic signal and the Hilbert transform,

@@

(s * r)_a (t) &= s * r + j ~ \widehat{s*r} \\
\mathcal{E}_{s * r}(t) &= | s * r + j s * r * h|

@@

However,

@@

r_a * s_a &= (r + j \hat{r}) * (s + j \hat{s}) \\
r_a * s_a &= r * s + j r * \hat{s} + j \hat{r} * s - \hat{r} * \hat{s} \\
r_a * s_a &= r * s - r * h * s * h + 2 j h * r * s \\
r_a * s_a &= r * s - h * h * r * s + 2 j h * r * s \\
r_a * s_a &= 2 r * s + 2 j h * r * s

@@

Multiplying both sides $1/2$ and taking the magnitude completes the proof:
\frac{1}{2} |r_a * s_a| = |r * s + j h * r * s| = \mathcal{E}_{s * r}(t) \\
\item The RLC damped oscillator impulse response and corresponding analytic signal are
r(t) &= R_0 e^{-2 \pi \gamma_f t} \cos(2\pi f_0 t) \label{eq:r} \\
r_a(t) &= R_0 e^{-2 \pi \gamma_f t} e^{2\pi j f_0 t} \label{eq:ra}
The parameters $\gamma_f$ and $f_0$ are the \textit{decay constant} that corresponds to the \textit{fall time} of the output signal, and the resonance frequency.  Note that the envelope of $r(t)$, $|r_a(t)|$, is $R_0 \exp(-2 \pi \gamma_f t)$, as expected.  To prove Eq. \ref{eq:ra}, first compute the Fourier transform of $r(t)$:
R(f) &= \frac{R_0}{4\pi j} \left( \frac{1}{f - z_{+}} + \frac{1}{1- z_{-}} \right) \\
z_{+} &= f_0 + j \gamma_f \\
z_{-} &= -f_0 + j \gamma_f
Given Eq. \ref{eq:sa_2}, the procedure to find $r_a(t)$ is to multiply the \textit{negative} frequency components by 0 and the \textit{positive} frequency components by 2, and take the inverse Fourier transform.  The inverse Fourier transform may be completed by extension to the complex plane using the upper infinite semi-circle as a contour, and applying Jordan's lemma.  The residue from the pole at $z_{+}$ drives the final result.
%\item The behavior of the RLC oscillator can be extended to the charging state, and the decaying state, via the time-reversal of Eq. \ref{eq:r}.  Times with $t\leq 0$ correspond to the charging state, $t=0$ corresponds to peak response, and $t\geq 0$ corresponds to the decaying state.  For the charging state:
%\begin{align}
%r(t) &= R_0 e^{2 \pi \gamma_r t} \cos(2\pi f_0 t) \label{eq:rc} \\
%r_a(t) &= R_0 e^{2 \pi \gamma_r t} e^{2\pi j f_0 t} \label{eq:rac}
%\end{align}
%The resonance frequency remains the same as the decaying state, and $\gamma_r$ corresponds to the \textit{rise time} in the same way that $\gamma_f$ corresponds to the \textit{fall time.}  In general, the rise and fall times do not have to be equal.

@@

r_a(t) * \Re\lbrace s_a(t) \rbrace = \int_0^{\infty} r_a(\tau) s(t-\tau) d\tau

@@

Substituting Eq. \ref{eq:fadd} into Eq. \ref{eq:conv}, and simplifying, produces

@@

-j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz} \label{eq:Re_result}

@@

\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= R_0\int_{0}^{\infty} e^{-z_0 t} e^{-2\pi j ft} dt \\

@@

\sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) - j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz} + \\
j\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + j\sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:final}

@@

The units of convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq. \ref{eq:final} has these units.  The first term is proportional to $R_0 \sigma_t s(t)$, and $s(t)$ has units of $E_0 \sigma_t$, so the unit product is $R_0 E_0\sigma_t^2$.  The units of the second term are $R_0 E_0\sigma_t^2$.  The third term has units of $E_0\sigma_t^2 r_a(t)$, and $r_a(t)$ has units of $R_0$, so the unit product is $R_0 E_0\sigma_t^2$.  The fourth term has units of $R_0 \sigma_t s(t)$, like the first term.  Thus, all units check.  To check the limits, the parameters within $z$ and $z_1$ must be recalled.  Combining prior definitions, the results are
